---
title: Evaluating effectiveness of controlling little seed canary grass by using chemical herbicides and allelopathic integration
author: "aminahadayat05@gmail.com"
date: "2023-02-21"
output:
  html_document:
    toc: yes
    toc_depth: 3
    toc_float:
      collapsed: no
      smooth_scroll: no
  md_document:
    variant: markdown_github
  pdf_document:
    toc: yes
    toc_depth: '3'
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  fig.width = 10,
  fig.asp=0.8,
  message = F,
  dpi = 300,
  collapse = TRUE,
  comment = "#>",
  fig.path = "figures/Figure-",
  fig.align = "center",
  out.width = "70%"
)
```

# Load packages

```{r packages}
library(tidyverse)
library(cowplot)
library(ggpubr)
library(pheatmap)
library(RColorBrewer)
library(vegan)
library(reshape2)
library(magrittr)
library(ggplot2)

theme_set(theme_bw())
```

To enable reproducible study, we provided the raw-data and source codes for analysis and generating figures. Figures and Figures were generated by the following R codes.

# Data processsing

Raw data were stored in the `data`` folder. It mainly comes from two experiments: one from growth room study, and the other is field experiment. The raw data is provided as in formatted form.

```{r}
weed_suppression <- read_csv("data/weed suppression.csv")
wheat_promotion <- read_csv("data/wheat promotion.csv")
weed_infestation <- read_csv("data/weed infestation.csv")
infested_wheat <- read_csv("data/infested wheat.csv")
head(weed_suppression)
head(wheat_promotion)
head(weed_infestation)
head(infested_wheat)
```
The columns are:

-   `herbicide_dose`: herbicide_doses, indicating the name of two different chemical herbicides (Atlantis and Axial) at 25 and 50% of recommended doses: i.e. "Herbicide control", "Atlantis 25%", "Atlantis 50%", "Axial 25%", "Axial 50%".
-
-   `Inoculation`: Inoculation indicating the combinations of four different Pseudomonas strains (B11, T19, T24, T75) collected from Soil microbiology biochemistry laboratory, University of Agriculture Faisalabad. "C1", "C2", "C3", "C4" represent the Pseudomonas strain combinations such as C1 (B11 x T75), C2 (T19 x T24), C3 (B11 x T24 x T75) and C4 (B11 x T19 x T24 x T75).
-   `treatments`: Under field condition nine treatments were planned in block plot for both weed infestation and infested wheat with weedy and wheat free control respectively, in order to evaluate the selected C4 combination along with Axial herbicide at four different recommended doses such as: 25, 50, 75, and 100% Axial with respective control treatments.   
                      

# Figure 1: Influence of AB combinations and chemical herbicides on P. minor growth and phenological parameter reduction in growth room trial {#fig-1}

```{r}
#Germination %
germination_percentage<-weed_suppression%>%select("herbicide_dose","Inoculation","seed_germination")
compare_means(seed_germination~Inoculation,data = germination_percentage,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p1<-ggboxplot(germination_percentage,x="Inoculation",y="seed_germination",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="seed_germination (%)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p1
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

##SPAD
SPAD<-weed_suppression%>%select("herbicide_dose","Inoculation","SPAD_value")
compare_means(SPAD_value~Inoculation,data = SPAD,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p2<-ggboxplot(SPAD,x="Inoculation",y="SPAD_value",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="SPAD_value",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p2
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

###Plant height
PH<-weed_suppression%>%select("herbicide_dose","Inoculation","plant_height")
compare_means(plant_height~Inoculation,data = PH,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p3<-ggboxplot(PH,x="Inoculation",y="plant_height",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="plant_height (cm)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p3
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

#####Root length
RL<-weed_suppression%>%select("herbicide_dose","Inoculation","root_length")
compare_means(root_length~Inoculation,data = RL,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p4<-ggboxplot(RL,x="Inoculation",y="root_length",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="root_length (cm)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p4
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

#####Fresh biomass
FB<-weed_suppression%>%select("herbicide_dose","Inoculation","fresh_biomass")
compare_means(fresh_biomass~Inoculation,data = FB,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p5<-ggboxplot(FB,x="Inoculation",y="fresh_biomass",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="fresh_biomass (g)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p5
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

######Protein
Pro<-weed_suppression%>%select("herbicide_dose","Inoculation","protein")
compare_means(protein~Inoculation,data = Pro,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p6<-ggboxplot(Pro,x="Inoculation",y="protein",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="protein (ppm)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p6
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

#######Chlorophyll a
Chla<-weed_suppression%>%select("herbicide_dose","Inoculation","chlorophyll_a")
compare_means(chlorophyll_a~Inoculation,data = Chla,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p7<-ggboxplot(Chla,x="Inoculation",y="chlorophyll_a",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="chlorophyll_a(ppm)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p7
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

########Chlorophyll b
Chlb<-weed_suppression%>%select("herbicide_dose","Inoculation","chlorophyll_b")
compare_means(chlorophyll_b~Inoculation,data = Chlb,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p8<-ggboxplot(Chlb,x="Inoculation",y="chlorophyll_b",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="chlorophyll_b (ppm)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p8
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

#########Croteniod
crot<-weed_suppression%>%select("herbicide_dose","Inoculation","caroteniod")
compare_means(caroteniod~Inoculation,data = crot,method = "t.test",group.by = "herbicide_dose")

#boxplot facet by "herbicide dose"
p9<-ggboxplot(crot,x="Inoculation",y="caroteniod",
             add = "jitter",
             facet.by = "herbicide_dose",short.panel.labs = FALSE)+
             labs(y="caroteniod (ppm)",x="Inoculation")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif",method = "t.test", ref.group = ".all.")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "top")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
p9
ggsave("figure 1.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

```

## Figure 2:application of Inoculation for testing either strains combinations have ability to enhance the growth of wheat or not {#fig-2}

```{r}
cols <- setdiff(names(wheat_promotion), 'Inoculations')
y_labels <- c("seed_germination (%)","plant_height (cm)", "Root_length (cm)","fresh_biomass (g)","SPAD_value","chlorophyll_a (ppm)","chlorophyll_b (ppm)","carotenoid (ppm)","protein (ppm)")
compare_means(seed_germination~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")
compare_means(plant_height~Inoculations,data = wheat_promotion,method = "anova")
compare_means(Root_length~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")
compare_means(fresh_biomass~Inoculations,data = wheat_promotion,method = "anova")
compare_means(SPAD_value~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")
compare_means(chlorophyll_a~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")
compare_means(chlorophyll_b~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")
compare_means(carotenoid~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")
compare_means(protein~Inoculations,data = wheat_promotion,ref.group="control",
              method = "t.test")

Map(function(x, y) {
  ggboxplot(data = wheat_promotion, x = "Inoculations", y = x,
            ylab = y, xlab = "Inoculations",
            add = "jitter")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif", method = "t.test",
                     ref.group = "control")+
    rotate_x_text(angle = 40)+
    theme(legend.position = "right")+
    theme(legend.title = element_text(color="black",size = 10,
                                      face = "bold"))+
    theme(legend.text = element_text(color = "black",size = 8))
    
}, cols, y_labels) -> list_plots
list_plots$seed_germination
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$plant_height
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$Root_length
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$fresh_biomass
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$SPAD_value
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$chlorophyll_a
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$chlorophyll_b
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$carotenoid
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_plots$protein
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

ggarrange(plotlist = list_plots,
          common.legend = TRUE,
          labels = c("A","B","C","D","E","F","G","H","I"))
ggsave("figure 2.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)


```


### Figure 3: weed infestation {#fig-3}

```{r}
cols <- setdiff(names(weed_infestation),'treatments')
y_labels <- c("total_weed_density m-2","no_of_native_weeds (%)", "shoot_length (cm)","SPAD_value","grain_yield (t ha-1)","straw_yield (t ha-1)","photosynthetic_rate (µmol m-2 s-1) ","transpiration_rate (µmol m-2 s-1)","stomatal_conductance (mmol m-2 s-1)")
compare_means(total_weed_density~treatments,data = weed_infestation,
              method = "anova")
compare_means(no_of_native_weeds~treatments,data = weed_infestation,
              method = "anova")
compare_means(shoot_length~treatments,data = weed_infestation,
              method = "anova")
compare_means(SPAD_value~treatments,data = weed_infestation,
              method = "anova")
compare_means(grain_yield~treatments,data = weed_infestation,
              method = "anova")
compare_means(straw_yield~treatments,data = weed_infestation,
              method = "anova")
compare_means(photosynthetic_rate~treatments,data = weed_infestation,
              method = "anova")
compare_means(transpiration_rate~treatments,data = weed_infestation,
              method = "anova")
compare_means(stomatal_conductance~treatments,data =weed_infestation,
              method = "anova")
Map(function(x, y) {
  ggboxplot(data = weed_infestation, x = "treatments", y = x,
            legend ="none",
            ylab = y, xlab = "treatments",
            bxp.errorbar = FALSE,
            bxp.errorbar.width = 0.4,
            notch = FALSE,
            add = "jitter")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif", method = "t.test",
                     ref.group = "weedy control")+
    scale_shape_manual(values =rep(15:18,5))+
    theme(legend.position =(0.5),
          legend.direction = "horizontal",
          legend.text = element_text(face = "italic"),
          legend.title = element_blank(),
          axis.text.x = element_text(angle = 30, hjust = 1,vjust = 1))

}, cols, y_labels) -> my_plots

my_plots$total_weed_density
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$no_of_native_weeds
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$shoot_length
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$SPAD_value
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$grain_yield
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$straw_yield
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$photosynthetic_rate
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$transpiration_rate
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

my_plots$stomatal_conductance
ggsave("figure 3.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

```



#### Figure 4: wheat infestation {#fig-4}

```{r}
cols <- setdiff(names(infested_wheat),'treatments')
y_labels <- c("shoot_length (cm)","SPAD_value", "no_of_tillers_plant-1","biological_yield","grain_yield (t ha-1)","straw_yield (t ha-1)","photosynthetic_rate (µmol m-2 s-1) ","transpiration_rate (µmol m-2 s-1)","stomatal_conductance (mmol m-2 s-1)")
compare_means(shoot_length~treatments,data = infested_wheat,method = "anova")
compare_means(SPAD_value~treatments,data = infested_wheat,method = "anova")
compare_means(no_of_tillers_per_plant~treatments,data = infested_wheat,method = "anova")
compare_means(biological_yield~treatments,data = infested_wheat,method = "anova")
compare_means(grain_yield~treatments,data = infested_wheat,method = "anova")
compare_means(straw_yield~treatments,data = infested_wheat,method = "anova")
compare_means(photosynthetic_rate~treatments,data = infested_wheat,method = "anova")
compare_means(transpiration_rate~treatments,data = infested_wheat,method = "anova")
compare_means(stomatal_conductance~treatments,data = infested_wheat,method = "anova")
Map(function(x, y) {
  ggboxplot(data = infested_wheat, x = "treatments", y = x,
            legend ="none",
            ylab = y, xlab = "treatments",
            bxp.errorbar = FALSE,
            bxp.errorbar.width = 0.4,
            notch = FALSE,
            add = "jitter")+
    stat_compare_means(method = "anova")+
    stat_compare_means(label = "p.signif", method = "t.test",
                     ref.group = "weed free control")+
    scale_shape_manual(values =rep(15:18,5))+
    theme(legend.position =(0.5),
          legend.direction = "horizontal",
          legend.text = element_text(face = "italic"),
          legend.title = element_blank(),
          axis.text.x = element_text(angle = 30, hjust = 1,vjust = 1))

}, cols, y_labels) -> list_of_plots

list_of_plots$shoot_length
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$SPAD_value
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$no_of_tillers_per_plant
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$biological_yield
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$grain_yield
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$straw_yield
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$photosynthetic_rate
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$transpiration_rate
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

list_of_plots$stomatal_conductance
ggsave("figure 4.tiff",path = "figures")
export::graph2ppt(file="figures.ppt",append=TRUE)

```


